Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-19 main.tex
Add affiliation and links to data.
Closes #13

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}
\usepackage{fancyvrb}

@@

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta E. Glynatsi \and
        Owen Campbell}
\date{}

@@

All data generated for this work is archived and available...
% TODO Add details once data is archived.
% TODO Include url to repo etc.

>>>>

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}
\usepackage{fancyvrb}
\usepackage{authblk}

@@

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author[1]{Marc Harper}
\author[2]{Vincent Knight}
\author[3]{Martin Jones}
\author[4]{Georgios Koutsovoulos}
\author[2]{Nikoleta E. Glynatsi}
\author[3]{Owen Campbell}

\affil[1]{Google Inc., Mountain View, CA, USA}
\affil[2]{Cardiff University, School of Mathematics, UK}
\affil[3]{Not affiliated}
\affil[4]{INRA, Université Côte d‘Azur, CNRS, ISA, France}
\date{}

@@

All data generated for this work is archived and available at~\cite{data}.
